Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-11-06 paper/ms.tex
new updates in reply to the referee

{\bf The second constraint is the angular correlation function
(ACF). {\bf \cite{Yamada2012} does not report an ACF measurement for the entire field}. Instead
we use the results by \cite{Hayashino2004} who has reported the ACF for the
first and at the same time the densest sub-field of  SSSA22 as we have mention 
before.

@@

%{\bf The LAEs number density inferred by \cite{Hayashino2004} is
 % $0.37$ arcmin$^{-2}$, which is $15\%$ lower than the new measurement
%by \cite{Yamada2012}. 
In the case of \cite{Ouchi2008} the number
density is $0.10$ arcmin$^{-2}$, which is $\sim 50\%$ than the value
inferred by \cite{Yamada2012} for a portion of the same region.}

\subsection{The adequacy of using SSA22 as an observational test}

{\bf The field centered on SSA22 has been known to harbor a 
  galaxy overdensity. Measurements of Lyman Break Galaxies show that
  the densest sub-field presents an overdensity 6 times the one present in a
  blank field \cite{XXX}. Using the data of \cite{Yamada2012}, we
  compute that for LAEs the whole region is only 1.4 times more dense than
  the blank fields of SXDS, SDF and GOODS-N. The densest sub-field
  in SSA22 is only 2 times denser than the average of the blank
  fields.}

{\bf This shows that the bias factor of LBGs is higher
  than LAEs. In a LCDM cosmology this implies that LAEs are, on average,
  hosted by halos less massive than those hosting LBGs. The
  interpretation of how rare is this subfield in terms of the number
  densities of dark matter halos has to assume a defined model for
  galaxy formation[...]}

{\bf Excluding the densest region in the SSA222, all the fields have a
similar number densisty as the blank fields and cannot be considered
as rare. The left panel in Figure \ref{fig:halos} shows the integrated
distritbution of LAEs number density in all the fields reported in
\cite{Yamada2012}.

From this figure it is clear that the highest density
sub-fields is the only outlier in the distribution. Therefore, using
as a benchmark the number density distribution that includes the
sub-fields in the SSA22 region does not impose a strong bias to select
very rare regions in a cosmological simulation. However, on has to
keep in mind that only very rarely the full number density distribution from a
simulation will include a very dense field as an outlier. We will not
require the presence of such field to judge a mock distribution as
successful. [...]}

>>>>

{\bf The second constraint is the angular correlation function
(ACF). {\bf \cite{Yamada2012} does not report an ACF measurement for
    the entire field. Instead we use the results by
  \cite{Hayashino2004} who has reported the ACF in the SSA22 region,
  including its densest subfield.}

@@

%{\bf The LAEs number density inferred by \cite{Hayashino2004} is
 % $0.37$ arcmin$^{-2}$, which is $15\%$ lower than the new measurement
%by \cite{Yamada2012}.

{\bf In the case of \cite{Ouchi2008} the number
density is $0.10$ arcmin$^{-2}$, which is $\sim 50\%$ than the value
inferred by \cite{Yamada2012} for a portion of the same region.}

\subsection{The adequacy of including SSA22 as an observational benchmark}

{\bf The field centered on SSA22 has been known to harbor a 
  galaxy overdensity. Measurements of Lyman Break Galaxies show that
  the densest sub-field presents an overdensity 6 times the one present in a
  blank field \cite{XXX}. Using the data of \cite{Yamada2012}, we
  compute that for LAEs the whole region is only 1.4 times more dense than
  the blank fields of SXDS, SDF and GOODS-N. The densest sub-field
  in SSA22 is 2 times denser than the average of the blank
  fields.}

{\bf Excluding the densest region in the SSA22, all the fields have a
similar number density as the blank fields and cannot be considered
as rare. The left panel in Figure \ref{fig:halos} shows the integrated
distribution of LAEs number density in all the fields reported in
\cite{Yamada2012}. It is evident that there is only one sub-field that
stands out as an outlier in the distribution (it corresponds to the
densest field in SSA22), the central message of this distribution is
that all the other fields form a continous distribution in number density.}

{\bf Therefore, using
as a benchmark the number density distribution that includes the
sub-fields in the SSA22 region does not impose a strong bias to select
very rare regions in a cosmological simulation. However, on has to
keep in mind that only very rarely the full number density distribution from a
simulation will include a very dense field as an outlier. We will not
require the presence of such field to judge a mock distribution as
successful. In terms of the ACF the results that include the densest
field in SSA22 \citep{Hayashino2004} are consistent, within the
uncertainties, with the results of other fields \citep{Ouchi2008}.}

{\bf Finally, two very different number densities in LBGs versus LAEs evidences
  that the two populations have different biases. In a $\Lambda$ CDM
  cosmology this implies that LAEs are, on average, hosted by halos
  less massive than those hosting LBGs. The interpretation of how rare
  is this subfield in terms of the number densities of dark matter
  halos has to assume a defined model for galaxy formation;
  i.e. defining the link between halo mass, star formation rate, \ly
  luminosity and \ly escape fraction.}

{\bf The purpose of our work is to avoid any loose of generality by
  assuming a defined halo-LAE connection and instead explore all the
  possible halo populations to host LAEs.}
